Capturing Policies for BYOD

### 2016-10-07 paper.tex
did barely anything yesterday. shame

>>>>

Corporate BYOD policies are tricky to fully enforce.
Part of their policies are prescriptive:  if you configure your device in this way you will mitigate that threat.
The policies contain more than just configuration, however.
Consider this rule taken from the \emph{Security Policy for the use of handheld devices in corporate environments} by SANS~\cite{nicholas_r._c._guerin_security_2008}:

\begin{quote}
  Digital camera embedded on handheld devices \emph{might} be disabled in restricted environments, according to $\langle$COMPANY NAME$\rangle$ risk analysis. 
  In sensitive facilities, information can be stolen using pictures and possibly sent using MMS or E-mail services.

  In high-security facilities such as R&D labs or design manufacturers, camera MUST be disabled.
  Furthermore, MMS messages should be disabled as well, to prevent malicious users from sending proprietary pictures.
\end{quote}
